Concentration Inequalities

### 2015-10-02 causal-bandit/observe_then_best.tex
updates known but unbalanced q case to get O(T^2/3 m^1/3) regret

\section{Bounding the Simple Regret}

@@

\subsubsection*{Regret during explore phase}
Since the probability we play each arm is constant and uniform during the exploration phase, the expected regret is simply proportional to the average sub-optimality $\Delta$.
\eqn{
R_1 = h\sum_i P(i)\Delta_i = \frac{h}{K}\sum_i \Delta_i = h E[\Delta]
}

@@

Without loss of generality, we can assume $q_i \in [0,\frac{1}{2}]$ and $q_1 \leq q_2 ... \leq q_N$. Let $m \in [2,N] = \{m:q_m > \frac{1}{m}\}$ Ie if the problem is completely balanced $q_1...q_N = \frac{1}{2}$ then $m = 2$. If the problem is completely unbalanced, $q_1...q_N = 0$ then $m=N$

@@

\eqn {
\hat{\mu}_{ij} = \frac{\sum_{t=1}^{h/2}\ind{Y=1,X_i=1}}{\frac{h}{2}q_{ij}}
}

@@

For these arms the Hoeffdings gives

\eqn{
P(\hat{\mu}_i - \mu_{i} > \frac{D}{2}) \leq e^{-hD^2/2m^2}
}

@@

\eqn{
P(\hat{\mu}_i - \mu_{i} > \frac{D}{2}) \leq e^{-hD^2/4m^2}
}

@@

\eqn{
\label{eqn:unbalancedHoeffdings}
P(\Delta_{\hat{i^*}} > D) \leq Ke^{-hD^2/4m^2}
}

If we let $D = \sqrt{\frac{4m^2\log(hK)}{h}}$

\eqn{
R_T  \leq h + T\left(\sqrt{\frac{4m^2\log(hK)}{h}} + \frac{1}{h}\right)
}

Let $h = T^{2/3}m^{2/3}\log(hk)$

\eqn {
R_T  \leq 4T^{\frac{2}{3}}m^{2/3}(log(KT))^{\frac{1}{3}}
}

Note, I think the $m^{2/3}$ should be improvable to something close to $m^{1/3}$ is I use Berstein's instead of Hoeffdings to bound the estimator for the arms where $q > 1/m$ but I haven't got the equations to quite work out for that yet.

@@

\subsection{Generalizing to unknown q}
We now consider the case where $\boldsymbol{q}$ is not known in advance. Assume as before that we observe for $h/2$ timesteps. From the observations gained in this phase we estimate $\boldsymbol{q}$.

>>>>

@@

\subsubsection*{Regret during explore phase}
Since the probability we play each arm is constant and uniform during the exploration phase, the expected regret is simply proportional to the average sub-optimality $\Delta$.
\eqn{
R_1 = h\sum_i P(i)\Delta_i = \frac{h}{K}\sum_i \Delta_i = h E[\Delta] < h
}

@@

Without loss of generality, we can assume $q_i \in [0,\frac{1}{2}]$ and $q_1 \leq q_2 ... \leq q_N$. Let $m \in [2,N] = \{m:q_m > \frac{1}{m}\}$ Ie if the problem is completely balanced $q_1...q_N = \frac{1}{2}$ then $m = 2$. If the problem is completely unbalanced, $q_1...q_N = 0$ then $m=N$. Let $q_{ij} = \P{X_i = j}$

@@

\eqn {
\hat{\mu}_{ij} = \frac{\sum_{t=1}^{h/2}\ind{Y_t=1,X_{t,i}=j}}{\frac{h}{2}q_{ij}}
}

@@

Let $Z_{t,ij} = \ind{Y_t=1,X_{t,i}=j} \sim Bernoulli(q_{ij}\mu_{ij})$,

Chernoff's inequality gives

\eqn{
P(\hat{\mu}_i - \mu_{i} > \frac{D}{2}) \leq e^{-hD^2/24m}
}

@@

\eqn{
P(\hat{\mu}_i - \mu_{i} > \frac{D}{2}) \leq e^{-hD^2/24m}
}

@@

\eqn{
\label{eqn:unbalancedHoeffdings}
P(\Delta_{\hat{i^*}} > D) \leq Ke^{-hD^2/24m}
}

If we let $D = \sqrt{\frac{24m\log(hK)}{h}}$

\eqn{
R_T &  \leq h + T\left(\sqrt{\frac{24m\log(hK)}{h}} + \frac{1}{h}\right) \\
& \leq h + T\left(\sqrt{\frac{24m\log(TK)}{h}} + \frac{1}{h}\right) 
}

Let $h = T^{2/3}m^{1/3}\log(TK)^{1/3}$

\eqn {
R_T & \leq 6T^{2/3}m^{1/3}log(KT)^{1/3} + T^{1/3}m^{-1/3}log(KT)^{-1/3}\\ 
& \leq 7T^{2/3}m^{1/3}log(KT)^{1/3}
}

@@

\subsection{Generalizing to unknown q}

\subsubsection{Bounding the Simple Regret}

We now consider the case where $\boldsymbol{q}$ is not known in advance. Assume as before that we observe for $h/2$ timesteps. From the observations gained in this phase we estimate $\boldsymbol{q}$.
